Flatiron cleaning

### 2022-02-24 Rmd/Adjusted weight rdi analysis.Rmd
Fix adjusted CrCl

IF actual_bmi >= 25 :
$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
IF actual_bmi < 25 :

@@

  mutate(actual_bmi = weight / (height * height)) %>%
  mutate(actual_bmi_cat = case_when(
    actual_bmi < 25                    ~ "Underweight and normal weight",
    actual_bmi >= 25 &
      actual_bmi < 30                  ~ "Overweight",
    actual_bmi >= 30                   ~ "Obese"
  )) %>%
  mutate(actual_bmi_cat = factor(actual_bmi_cat, 
                                  levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
  # select(patientid, weight, height, bmi_at_dx, ideal_weight, adjusted_weight, adjusted_bmi)
  # Calculate CrCl
  # inner_join(., clinical_data %>% select(-surgerydate),
  #            by = "patientid") %>% 
  mutate(CrCl = (
       (
    ((140 - ageatdx) * weight) /
    (72 * creatinine)
       ) *
    0.85)
  ) %>% 
  mutate(CrCl = case_when(
    CrCl > 125                        ~ 125,
    TRUE                              ~ CrCl
  )) %>% 
  mutate(adjusted_CrCl = case_when(
    actual_bmi >= 25                  ~ CrCl,
    actual_bmi < 25                   ~ (((140 - ageatdx) * adjusted_weight) / (72 * creatinine)) * 0.85
  )) %>% 
  mutate(adjusted_CrCl = case_when(
    adjusted_CrCl > 125               ~ 125,
    TRUE                              ~ adjusted_CrCl
  )) %>%

@@

  # Calculate expected dose
  mutate(expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
    drugname == "paclitaxel"                  ~ BSA * target_auc 
    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  )) %>% 
  mutate(expected_dose = case_when(
    expected_dose > 900 &
      target_auc == 6              ~ 900,
    expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ expected_dose
  )) %>% 
  mutate(adjusted_expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25),
    drugname == "paclitaxel"                  ~ BSA * target_auc 
    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  )) %>% 
  mutate(adjusted_expected_dose = case_when(
    adjusted_expected_dose > 900 &
      target_auc == 6              ~ 900,
    adjusted_expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ adjusted_expected_dose
  )) %>% 
  group_by(patientid) %>%
  mutate(first_treatment_date = case_when(
    str_detect(therapy, "Chemo")                      ~ min(episodedate),
    str_detect(therapy, "Surgery")                    ~ surgerydate,
  )) %>% 
  ungroup() %>% 
  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
                   duration(n=1, units = "months")) %>% 
  arrange(patientid, episodedate)

>>>>

IF actual_bmi < 25 :
$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
IF actual_bmi >= 25 :

@@

  mutate(actual_bmi = weight / (height * height)) %>%
  mutate(actual_bmi_cat = case_when(
    actual_bmi < 25                    ~ "Underweight and normal weight",
    actual_bmi >= 25 &
      actual_bmi < 30                  ~ "Overweight",
    actual_bmi >= 30                   ~ "Obese"
  )) %>%
  mutate(actual_bmi_cat = factor(actual_bmi_cat, 
                                  levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
  # select(patientid, weight, height, bmi_at_dx, ideal_weight, adjusted_weight, adjusted_bmi)
  # Calculate CrCl
  mutate(CrCl = (
       (
    ((140 - ageatdx) * weight) /
    (72 * creatinine)
       ) *
    0.85)
  ) %>% 
  mutate(CrCl = case_when(
    CrCl > 125                        ~ 125,
    TRUE                              ~ CrCl
  )) %>% 
  mutate(adjusted_CrCl = case_when(
    actual_bmi < 25                   ~ CrCl,
    actual_bmi >= 25                  ~ (((140 - ageatdx) * adjusted_weight) / (72 * creatinine)) * 0.85
  )) %>% 
  mutate(adjusted_CrCl = case_when(
    adjusted_CrCl > 125               ~ 125,
    TRUE                              ~ adjusted_CrCl
  )) %>%

@@

  # Calculate expected dose
  mutate(expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
    drugname == "paclitaxel"                  ~ BSA * target_auc 
  )) %>% 
  mutate(expected_dose = case_when(
    expected_dose > 900 &
      target_auc == 6              ~ 900,
    expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ expected_dose
  )) %>% 
  mutate(adjusted_expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25),
    drugname == "paclitaxel"                  ~ BSA * target_auc 
  )) %>% 
  mutate(adjusted_expected_dose = case_when(
    adjusted_expected_dose > 900 &
      target_auc == 6              ~ 900,
    adjusted_expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ adjusted_expected_dose
  )) %>% 
  group_by(patientid) %>%
  mutate(first_treatment_date = case_when(
    str_detect(therapy, "Chemo")                      ~ min(episodedate),
    str_detect(therapy, "Surgery")                    ~ surgerydate,
  )) %>% 
  ungroup() %>% 
  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
                   duration(n=1, units = "months")) %>% 
  arrange(patientid, episodedate)
